---
title: "OCS Search"
output: html_document
runtime: shiny
weight: 2
---

Geturls
```{r, echo = FALSE, comments = FALSE, warning = FALSE, include = FALSE}
library(dplyr)
library(purrr)
library(tidyr)
library(fs)
library(rlang)
library(pkgdown)
library(glue)
library(stringr)
library(DT)
library(widgetframe)
library(tidyverse)

get_pkgdown_urls <-
  function(x, pth = tempdir(), fltr = "[\\s\\S]*") {
    pkg_name <- x$pkg

    x <- mutate(x, base_url = paste0(base_url, "reference/"))

    base_url <- paste0(x$base_url, "{file}")
    null_res <-
      tibble::tibble(
        topic = rlang::na_chr,
        title = rlang::na_chr,
        url = rlang::na_chr,
        pkg = pkg_name
      )
    src_file <-
      download.packages(pkg_name, destdir = pth, repos = "https://cran.rstudio.com/")
    if (nrow(src_file) != length(pkg_name)) {
      found <- src_file[, 1]
      lost <- pkg_name[!(pkg_name %in% found)]
      lost <- paste0("'", lost, "'", collapse = ", ")
      msg <- paste("packages", lost, "were not downloaded")
      rlang::abort(msg)
    }
    untar_res <- purrr::map_int(src_file[, 2], untar, exdir = pth)
    if (any(untar_res != 0)) {
      msg <- paste("packages",
                   paste0("'", pkg_name[untar_res != 0], "'", collapse = ", "),
                   "did not unpack correctly")
      rlang::abort(msg)
    }

    topic_info <-
      purrr::map(pkg_name, ~ pkgdown::as_pkgdown(fs::path(pth, .x))) %>%
      purrr::map( ~ pluck(.x, "topics")) %>%
      purrr::map2(pkg_name, ~ .x %>% mutate(pkg = .y)) %>%
      bind_rows()  %>%
      unnest(cols = c(alias)) %>%
      full_join(x, by = "pkg") %>%
      mutate(url = map2_chr(base_url, file_out, paste0),
             topic = alias) %>%
      dplyr::select(topic, alias, title, url, pkg) %>%
      mutate(title = str_replace(title, "\\n", " ")) %>%
      dplyr::filter(str_detect(topic, fltr)) %>%
      na.omit() %>%
      dplyr::filter(
        str_detect(topic, "reexport", negate = TRUE),
        str_detect(topic, "-package$", negate = TRUE),
        str_detect(title, "^Internal", negate = TRUE),
        str_detect(title, "^Tidy eval", negate = TRUE),
        topic != "_PACKAGE",
        title != "Pipe",
        topic != "%>%",
        title != "Objects exported from other packages"
      ) %>%
      dplyr::arrange(topic, pkg) %>%
      mutate(topic = paste0("<a href='", url,
                            "'  target='_blank'><tt>",
                            topic, "</tt></a>")
      ) %>%
      dplyr::select(topic, package = pkg, title, alias)

    topic_info
  }
```

To learn about the parsnip package, see [*Get Started: Build a Model*](/start/models/). Use the tables below to find [model types and engines](#models) and to explore [model arguments](#model-args).

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  digits = 3,
  collapse = TRUE,
  comment = "#>"
  )
options(digits = 3)
#script <- here::here("content/home/get_pkgdown_urls.R")
#source(script)
library(DT)
library(tibble)
pkgs <- 
  tibble(
    pkg = c("parsnip", "discrim", "poissonreg", "plsmod", "baguette", 
            "rules", "modeltime"), 
    base_url = case_when(pkg == "modeltime" ~ "https://business-science.github.io/modeltime/",
                         TRUE ~ paste0("https://", pkg, ".tidymodels.org/"))
  )
library(discrim)
library(parsnip)
library(poissonreg)
library(baguette)
library(rules)
library(modeltime)
library(widgetframe)
```



## Explore models {#models}

```{r model-table, echo = FALSE}
mod_names <- get_from_env("models")
model_info <-
  map_dfr(mod_names, ~ get_from_env(paste0(.x, "_predict")) %>% mutate(alias = .x))
model_modes <- 
  model_info %>% 
  distinct(alias, mode) %>% 
  group_by(alias) %>% 
  summarize(mode = paste0(sort(mode), collapse = ", "))
model_eng <- 
  model_info %>% 
  distinct(alias, engine) %>% 
  group_by(alias) %>% 
  summarize(engine = paste0("<tt>", sort(engine), "</tt>", collapse = ", "))
pkg_urls <- 
  get_pkgdown_urls(pkgs) %>% 
  dplyr::filter(alias %in% mod_names) %>% 
  mutate(title = str_remove(title, "General Interface for ")) %>% 
  full_join(model_modes, by = "alias") %>% 
  full_join(model_eng, by = "alias") %>% 
  dplyr::select(-alias) %>% 
  select(title, topic, package, mode, engine)
```


```{r table-display, echo = FALSE}
pkg_urls %<>% 
  mutate(
    package = as.factor(package),
    mode = as.factor(mode)
  ) %>%
  rename(`model type`=topic ) %>%
  DT::datatable(
    rownames = FALSE,
    class = 'cell-border stripe',
    escape = FALSE,
    filter = "top",
    options = list(pageLength = 5)
  )
widgetframe::frameWidget(pkg_urls)
```

<br>

Models can be added by the user too. The article [How to build a parsnip model](/learn/develop/models/) walks you through the steps.

## Explore model arguments {#model-args}

The parsnip package provides consistent interface for working with similar models across different engines. This means that parsnip adopts standardized parameter names as arguments, and those names may be different from those used by the individual engines. The searchable table below provides a mapping between the parsnip and the engine arguments: 

<br>

```{r}

```

```{r params, echo = FALSE, results = "asis", include = FALSE, eval = FALSE}
envir <- parsnip::get_model_env()
args <- 
  ls(envir) %>% 
  tibble(name = .) %>% 
  filter(str_detect(name, "args")) %>% 
  mutate(model = str_replace(name, "_args", ""),
         args  = map(name, ~envir[[.x]])) %>% 
  unnest(args) %>% 
  select(model:original) %>%
  rename(`model type`=model )
DT::datatable(
  args, 
  rownames = FALSE,
  class = 'cell-border stripe',
  filter = 'top',
  escape = FALSE,
  options = list(pageLength = 5)
  )

widgetframe::frameWidget(args)
```

